\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}

### 2010-03-16 AffineLieAlgebras/InformalNotes/article.tex
Some work on semisimple affine algebras

\documentclass[a4paper,12pt]{article}
\usepackage{ucs}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{pb-diagram}

%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}

@@

\newtheorem{statement}{Statement}
\theoremstyle{definition} \newtheorem{Def}{Definition}

@@

Consider affine Lie algebras $\frak{g}$ and $\frak{a}$ with the
underlying finite-dimensional subalgebras $\overset{\circ }{\frak{g}}$ and $%
\overset{\circ }{\frak{a}}$ and an injection $\frak{a}\longrightarrow \frak{g%
}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$ with
correlated root spaces: $\frak{h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g%
}}^{\ast }$ and $\frak{h}_{\overset{\circ }{\frak{a}}}^{\ast }\subset \frak{h%
}_{\overset{\circ }{\frak{g}}}^{\ast }$\ .

@@

$\overset{\circ }{\Delta }$ , $\left( \overset{\circ }{\Delta _{\frak{a}}}%
\right) $ --- the finite root system of the subalgebra $\overset{\circ }{%
\frak{g}}$ (resp. $\overset{\circ }{\frak{a}}$);
$\Theta$, $(\Theta_{\mathfrak{a}})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\mathfrak{a}$);

@@

$\overset{\circ }{\xi }$ , $\overset{\circ }{\xi _{\left( \frak{a}\right) }}$
--- the finite (classical) part of the weight $\xi \in P$ , $\left( \text{%
resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}\right) $;

$\lambda =\left( \overset{\circ }{\lambda };k;n\right) $ --- the
decomposition of an affine weight indicating the finite part $\overset{\circ
}{\lambda }$, level $k$ and grade $n$\ .

@@

$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
\xi \in P$ $\left( \text{resp. }\in P_{\frak{a}}\right) $ for the module $%
L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) $ with the
coordinates $\left( \overset{\circ }{\xi },k,n,\epsilon \left( w\left( \xi
\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
)-\rho },$ (resp. $\left( \overset{\circ }{\xi },k,n,\epsilon \left(
w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
\circ (\nu +\rho _{a})-\rho _{a}}$ ), (this set is similar to $P_{\mathrm{%
nice}}^{\prime }\left( \mu \right) $ in \cite{wakimoto2001idl})

@@

To get the recurrent relations for the anomalous branching coefficients we use the following procedure  (similar to that in \cite{ilyin812pbc}).
Let $\gamma_{0} $ be the lowest vector with respect to the natural ordering in $%
\overset{\circ }{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$ and decompose the defining relation (\ref{eq:11}),
\begin{equation}
  \label{eq:18}
  \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})}\left(
    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
      }}\mathrm{\left( \alpha \right) }}=-s\left( \gamma _{0}\right) e^{-\gamma
    _{0}}-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}\setminus \left\{\gamma_{0}\right\}}s\left( \gamma \right) e^{-\gamma },
\end{equation}
then the equality (\ref{eq:17}) leads to the desired recurrent  relation for the anomalous branching coefficients:
\begin{multline}
  k_{\xi }^{\left( \mu \right) }=
  -\frac{1}{s\left( \gamma _{0}\right) }
  \left(
    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}
    \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
    \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
    \right.\\
    \left. +
    \sum_{\gamma \in \Gamma _{\frak{a}\subset \frak{g}}} s\left( \gamma +\gamma _{0}\right) k_{\xi+\gamma }^{\left( \mu \right) }
  \right)
\label{recurrent relation}
\end{multline}
where the set
\begin{equation}
\Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} 
\label{fan-defined}
\end{equation}
 was introduced that is called the injection fan.

@@

We use the recurrent relation \eqref{recurrent relation} to formulate an algorithm for recursive computation of the branching coefficients. It is important to mention that the computation of the branching coefficients is performed without the  explicit construction of the module $L^{(\mu)}_{\mathfrak{g}}$ and any of the modules $L^{(\nu)}_{\mathfrak{a}}$.

The algorithm contains the following steps.
\begin{enumerate}
\item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{a} \subset \mathfrak{g}$.
\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
\item Construct the set $\Gamma$ \eqref{fan-defined}.
\item Calculate the anomalous branching coefficients in the main Weyl
  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent relation}).
\end{enumerate}

@@

Using the definition (\ref{fan-defined}) we get the following set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
\begin{figure}[h!tb]
  \includegraphics[width=130mm]{B4_B2_fan.pdf}
  \caption{Fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
We use the recurrent relation (\ref{recurrent relation}) and get
following branching coefficients:
\begin{equation}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}
\end{equation}
The dimension of the highest-weight $B_4$-module $L^{(0,1,0,2)}_{B_4}$
is equal to 2772. It is easy to see, that right-hand side of the
equation (\ref{eq:24}) gives the same result.

@@

In the decomposition (\ref{eq:3}) let the highest weight $\nu$ of the subalgebra module belong to the grade $n$ of the projected  module $\pi_{\mathfrak{a}}\cdot L^{(\mu)}_{\mathfrak{g}}$.  Then the relation (\ref{eq:111}) implies the following requirement on the conformal dimensions of the corresponding fields
\begin{equation}
  \label{eq:32}
   \Delta_{\pi_{\mathfrak{a}}\mu}+n=\Delta_{\nu}
\end{equation}
It leads to a restriction imposed on the classical parts of the corresponding weights:
\begin{equation}
  \label{eq:33}
  \frac{(\overset{\circ }{\mu},\overset{\circ }{\mu}+2\rho)}{2(1+g)}+n=\frac{(\overset{\circ }{\nu},\overset{\circ }{\nu}+2\rho_{\mathfrak{a}})}{2(x_e+a)}
\end{equation}
The finite reducibility theorem states that for conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.

@@

Embedding of affine extensions of semisimple subalgebras to affine lie algebras allows additional construction of modular invariants \cite{difrancesco1997cft}, \cite{walton1989conformal}. Consider the conformal embedding constructed as the affine extension  $\mathfrak{a}_{1}\oplus\mathfrak{a}_{2}\subset \mathfrak{g}$ of the embedding of semisimple subalgebra $\overset{\circ}{\mathfrak{a}}_1\oplus\overset{\circ}{\mathfrak{a}}_2$ into simple Lie algebra $\overset{\circ}{\mathfrak{g}}$.

@@

Consider the embedding $\widehat{su(2)\oplus su(2)}\subset \hat{su(4)}$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$. Let's construct the special embedding $su(2)\oplus su(2)\subset su(4)$ using the method of \cite{vasilevich1986method}. We start with 4-dimensional representation of $su(2)\oplus su(2)$ with the highest weight $(1,1)$.

, depicted at the Figure \ref{fig:a1a2a3}. This embedding is characterised by the embedding indexes $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.

Four dominant weights of level one have the following coordinates in the orthogonal basis: 
\begin{equation}
  \begin{array}{lll}
     \omega_0 & = & (0,0,0,0;1;0)\\
     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
  \end{array}
\end{equation}
We limit our computation by the fifth grade.
The set of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements.

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage{ucs}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}

@@

\newtheorem{statement}{Statement}
\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\go}{\overset{\circ }{\frak{g}}}
\newcommand{\ao}{\overset{\circ }{\frak{a}}}
\newcommand{\co}[1]{\overset{\circ }{#1}}

@@

Consider affine Lie algebras $\frak{g}$ and $\frak{a}$ with the
underlying finite-dimensional subalgebras $\go$ and $%
\ao$ and an injection $\frak{a}\longrightarrow \frak{g%
}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$ with
correlated root spaces: $\frak{h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g%
}}^{\ast }$ and $\frak{h}_{\ao}^{\ast }\subset \frak{h%
}_{\go}^{\ast }$\ .

@@

$\co{\Delta}$ , $\left( \co{\Delta _{\frak{a}}}%
\right)$ --- the finite root system of the subalgebra $\co{%
\frak{g}}$ (resp. $\co{\frak{a}}$);
$\Theta$, $(\Theta_{\mathfrak{a}})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\mathfrak{a}$);

@@

$\co{\xi }$ , $\co{\xi _{\left( \frak{a}\right) }}$
--- the finite (classical) part of the weight $\xi \in P$ , $\left( \text{%
resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}\right) $;

$\lambda =\left( \co{\lambda };k;n\right) $ --- the
decomposition of an affine weight indicating the finite part $\co{\lambda }$, level $k$ and grade $n$\ .

@@

$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
\xi \in P$ $\left( \text{resp. }\in P_{\frak{a}}\right) $ for the module $%
L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) $ with the
coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
\circ (\nu +\rho _{a})-\rho _{a}}$ ), (this set is similar to $P_{\mathrm{%
nice}}^{\prime }\left( \mu \right) $ in \cite{wakimoto2001idl})

@@

To get the recurrent relations for the anomalous branching coefficients we use the following procedure  (similar to that in \cite{ilyin812pbc}).
Let $\gamma_{0} $ be the lowest vector with respect to the natural ordering in $%
\co{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$ and decompose the defining relation (\ref{eq:11}),
\begin{equation}
  \label{eq:18}
  \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})}\left(
    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
      }}\mathrm{\left( \alpha \right) }}=-s\left( \gamma _{0}\right) e^{-\gamma
    _{0}}-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}\setminus \left\{\gamma_{0}\right\}}s\left( \gamma \right) e^{-\gamma },
\end{equation}
then the equality (\ref{eq:17}) leads to the desired recurrent  relation for the anomalous branching coefficients:
\begin{multline}
  k_{\xi }^{\left( \mu \right) }=
  -\frac{1}{s\left( \gamma _{0}\right) }
  \left(
    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}
    \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
    \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
    \right.\\
    \left. +
    \sum_{\gamma \in \Gamma _{\frak{a}\subset \frak{g}}} s\left( \gamma +\gamma _{0}\right) k_{\xi+\gamma }^{\left( \mu \right) }
  \right)
\label{recurrent-relation}
\end{multline}
where the set
\begin{equation}
\Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} 
\label{fan-defined}
\end{equation}
 was introduced that is called the injection fan.

@@

We use the recurrent relation \eqref{recurrent-relation} to formulate an algorithm for recursive computation of the branching coefficients. It is important to mention that the computation of the branching coefficients is performed without the  explicit construction of the module $L^{(\mu)}_{\mathfrak{g}}$ and any of the modules $L^{(\nu)}_{\mathfrak{a}}$.

The algorithm contains the following steps.
\begin{enumerate}
\item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{a} \subset \mathfrak{g}$.
\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
\item Construct the set $\Gamma$ \eqref{fan-defined}.
\item Calculate the anomalous branching coefficients in the main Weyl
  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent-relation}).
\end{enumerate}

@@

Using the definition (\ref{fan-defined}) we get the following set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
\begin{figure}[h!tb]
  \includegraphics[width=130mm]{B4_B2_fan.pdf}
  \caption{Fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
We use the recurrent relation (\ref{recurrent-relation}) and get
following branching coefficients:
\begin{equation}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}
\end{equation}
The dimension of the highest-weight $B_4$-module $L^{(0,1,0,2)}_{B_4}$
is equal to 2772. It is easy to see, that right-hand side of the
equation (\ref{eq:24}) gives the same result.

@@

In the decomposition (\ref{eq:3}) let the highest weight $\nu$ of the subalgebra module belong to the grade $n$ of the projected  module $\pi_{\mathfrak{a}}\cdot L^{(\mu)}_{\mathfrak{g}}$.  Then the relation (\ref{eq:111}) implies the following requirement on the conformal dimensions of the corresponding fields
\begin{equation}
  \label{eq:32}
   \Delta_{\pi_{\mathfrak{a}}\mu}+n=\Delta_{\nu}
\end{equation}
It leads to a restriction imposed on the classical parts of the corresponding weights:
\begin{equation}
  \label{eq:33}
  \frac{(\co{\mu},\co{\mu}+2\rho)}{2(1+g)}+n=\frac{(\co{\nu},\co{\nu}+2\rho_{\mathfrak{a}})}{2(x_e+a)}
\end{equation}
The finite reducibility theorem states that for conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.

@@

Embedding of affine extensions of semisimple subalgebras to affine lie algebras allows additional construction of modular invariants \cite{difrancesco1997cft}, \cite{walton1989conformal}. Consider the conformal embedding constructed as the affine extension  $\mathfrak{a}_{1}\oplus\mathfrak{a}_{2}\subset \mathfrak{g}$ of the embedding of semisimple subalgebra $\ao_1\oplus\ao_2$ into simple Lie algebra $\go$.

@@

Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\widehat{su(2)\oplus su(2)}$ and $\mathfrak{g}= \widehat{su(4)}$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$. Let's construct the special embedding $su(2)\oplus su(2)\subset su(4)$ using the method of \cite{vasilevich1986method}. We start with 4-dimensional representation of $su(2)\oplus su(2)$ with the highest weight $(1,1)$. The weights of this representation are numbered as depicted at the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1), \nu_2=(-1,1), \nu_3=(1,-1), \nu_4=(-1,-1)$.

\begin{figure}[t]
  \begin{multicols}{2}
    \hfill
    \includegraphics[width=50mm]{A_1+A_1_to_A3.pdf}
    \hfill
    \caption{Representation for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
    \label{fig:A_1+A_1_to_A3}
    \hfill
    \includegraphics[width=50mm]{A1+A1-A3.pdf}
    \hfill
    \caption{Embedded roots for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
    \label{fig:A1+A1-A3}
  \end{multicols}
\end{figure}

Then for the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method}, so $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.  The embedded roots $\alpha_1,\alpha_2$ of $su(2)\oplus su(2)$ in terms of roots $\tilde{\alpha}_i$ of $su(4)$ are
\begin{equation}
  \label{eq:37}
  \begin{array}{l}
     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
  \end{array}
\end{equation}
They are depicted at the Figure \ref{fig:A1+A1-A3}.

This embedding is characterised by the embedding indexes $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.

We are interested in the reduction of the fundamental representations of $\widehat{su(4)}$.
Four dominant weights of level one have the following coordinates in the orthogonal basis: 
\begin{equation}
  \begin{array}{lll}
     \omega_0 & = & (0,0,0,0;1;0)\\
     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
  \end{array}
\end{equation}

These representation could be easily reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras, but we use our general method and discuss its features.

For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
\begin{equation}
  \label{eq:38}
  \begin{array}{lll}
    \Delta^{+} &=&\left\{\co{\Delta}^{+};\; \co{\Delta}-n\delta;\;     -n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right. \\
    & & \quad\left.\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\}\right\}\\
    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm \alpha_2-n\delta;\; -n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
  \end{array}
\end{equation}

The set $\Delta^{+}_{\bot}$ is empty. 
\begin{enumerate}
\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
\item Construct the set $\Gamma$ \eqref{fan-defined}.
\item Calculate the anomalous branching coefficients in the main Weyl
  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent-relation}).
\end{enumerate}

We limit our computation by the fifth grade.
The set of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements.
